Making Sequential Programs Deterministic

### 2019-04-05 experiments.tex
Capitalization

The state of the art in flaky test detection is NonDex~\cite{nondex}.
\Cref{sec:related} explains how NonDex works. In this section, we perform a qualitative comparison of the
errors reported by NonDex and those reported by \TheDeterminismChecker. We ran all our
experiments on a 2.3 GHz Intel Core i5 processor with a RAM configuration of 8 GB 2133 MHz.
\TheDeterminismChecker doesn't show any noticeable performance change at compile time.
\TheDeterminismChecker runs on any project that builds with maven or gradle and requires
Java version 8 or higher (support for annotations was added in Java 8).

@@

We modified Randoop by deleting tests that were skipped by its buildfile,
because the NonDex gradle plugin does not respect those settings. 
After that, NonDex ran without problems on Randoop.
It completed successfully without reporting any flaky tests.
We investigated the tests covering code that \theDeterminismChecker reported as nondeterministic.
Bug 1 and Bug 2 have corresponding test cases whereas Bug 3 does not.
As NonDex is a \textit{flaky test} detection tool, Bug 3 is outside of its scope.
The reason for nondeterminism in Bug 2 was a call to the \<System.getProperty()> method which
is not modeled by NonDex.
This indicates that the additional programmer effort required by \TheDeterminismChecker is justified
as our tool discovers non-trivial issues and doesn't depend on code coverage or other runtime heuristics.

@@

\section{Comparison to Deflaker}
Deflaker~\cite{deflaker}, like NonDex, reports tests that could be flaky. 
While we would have like to run DeFlaker on Randoop for a fair comparison of the tools,
we were unable to do so because Deflaker works with projects built with maven and Randoop
uses gradle for its build system. We plan to convert Randoop's build system to maven and 
perform this case study.
%Ideally, we would have 
%liked to run all three tools (NonDex, DeFlaker, and \TheDeterminismChecker) on an open source project
%that wasn't explored by any of the tool for a fair comparison. Unfortunately, there are issues with the
%DeFlaker plugin and we weren't able to run it on any project. We have created a Github issue for the same
%in its repository.
%\todo{Deflaker works now. Tried on retrofit: only works where there is sufficient change in code coverage between head and its parent.
%Looked throught= about 10 commits, didn't find differential code coverage and therefore no flakes}
%\todo{Deflaker requires maven build. Randoop is on gradle.}

>>>>

The state of the art in flaky test detection is NonDex~\cite{nondex}.
\Cref{sec:related} explains how NonDex works. This section compares the
errors reported by NonDex and \theDeterminismChecker. We ran all our
experiments on a 2.3 GHz Intel Core i5 processor with a RAM configuration of 8 GB 2133 MHz.
\TheDeterminismChecker doesn't show any noticeable performance change at compile time.
\TheDeterminismChecker runs on any project that builds with Maven or Gradle and requires
Java version 8 or higher (support for annotations was added in Java 8).

@@

We modified Randoop by deleting tests that were skipped by its buildfile,
because the NonDex Gradle plugin does not respect those settings.
After that, NonDex ran without problems on Randoop.
It completed successfully without reporting any flaky tests.
We investigated the tests covering code that \theDeterminismChecker reported as nondeterministic.
Bug 1 and Bug 2 have corresponding test cases whereas Bug 3 does not.
As NonDex is a \textit{flaky test} detection tool, Bug 3 is outside of its scope.
The reason for nondeterminism in Bug 2 was a call to the \<System.getProperty()> method which
is not modeled by NonDex.
This indicates that the additional programmer effort required by \TheDeterminismChecker is justified
as our tool discovers non-trivial issues and doesn't depend on code coverage or other runtime heuristics.

@@

\section{Comparison to Deflaker}
Deflaker~\cite{deflaker}, like NonDex, reports tests that could be flaky. 
While we would have like to run DeFlaker on Randoop for a fair comparison of the tools,
we were unable to do so because Deflaker works with projects built with Maven and Randoop
uses Gradle for its build system. We plan to convert Randoop's build system to Maven and
perform this case study.
%Ideally, we would have 
%liked to run all three tools (NonDex, DeFlaker, and \TheDeterminismChecker) on an open source project
%that wasn't explored by any of the tool for a fair comparison. Unfortunately, there are issues with the
%DeFlaker plugin and we weren't able to run it on any project. We have created a Github issue for the same
%in its repository.
%\todo{Deflaker works now. Tried on retrofit: only works where there is sufficient change in code coverage between head and its parent.
%Looked throught= about 10 commits, didn't find differential code coverage and therefore no flakes}
%\todo{Deflaker requires Maven build. Randoop is on Gradle.}
